CKY Parsing With Independence Constraints

### 2015-05-16 paper.tex
Remove some unnecessary stuff
Make appendix an actual appendix

% Created 2015-05-16 Sat 13:06
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage{hyperref}
\tolerance=1000
\usepackage{acl2015}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage{forest}
\usepackage[linesnumbered]{algorithm2e}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\newcommand{\BigO}[1]{\ensuremath{\operatorname{O}\bigl(#1\bigr)}}
\date{\today}
\title{CKY Parsing With Independence Constraints}
\hypersetup{
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs 24.4.1 (Org mode 8.2.10)}}
\begin{document}

@@

The derivations of Equations 1-3 are shown in the appendix.

@@

\section{Appendix}
\label{sec-8}

\subsection{Derivation of equations in section \ref{sec:comp-saved}}
\label{sec-8-1}

@@

\subsection{Detailed parse results}
\label{sec-8-2}

@@

\bibliographystyle{acl}
\bibliography{references}
% Emacs 24.4.1 (Org mode 8.2.10)
\end{document}

>>>>

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage{acl2015}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage{forest}
\usepackage[linesnumbered]{algorithm2e}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\newcommand{\BigO}[1]{\ensuremath{\operatorname{O}\bigl(#1\bigr)}}
\date{\today}
\title{CKY Parsing With Independence Constraints}
\begin{document}

@@

The derivations of Equations 1-3 are shown in Appendix~\ref{sec:derivation-equations}.

@@

\appendix
%% \section{Appendix}
\label{sec-8}

\section{Derivation of equations in section \ref{sec:comp-saved}}
\label{sec:derivation-equations}

@@

\section{Detailed parse results}
\label{sec-8-2}

@@

\bibliographystyle{acl}
\bibliography{references}
\end{document}
